Cross Entropy Clustering
========================================================

Part of [gmum.R project](http://r.gmum.net). See also [gmum research group page](http://gmum.net).

General
------

CEC aims to efficiently implement Cross Entropy Clustering algorithm as R extension.

More about CEC in the paper:
[Tabor, J., & Spurek, P. (2014). Cross-entropy clustering. Pattern Recognition, 47(9), 3046-3059.](http://www.sciencedirect.com/science/article/pii/S0031320314000764)

CEC demo
------

```{r fig.width=7, fig.height=6}
library(devtools)
library('gmum.r')

data(cec_mouse_1_spherical)
dataset = cec_mouse_1_spherical.input
```
That is the dataset we want to cluster:
```{r fig.width=7, fig.height=6}
plot(dataset, main="Mouse-like dataset")
```

Run CEC with default parameters. Set number of clusters and dataset.

```{r fig.width=7, fig.height=6}
c <- CEC(k=3, x=dataset)
plot(c)
```

Since initial clusterization is random. It may be a good idea to run CEC multiple times and choose the best result.

```{r fig.width=7, fig.height=6}
c <- CEC(k=3, x=dataset, control.nstart=10)
plot(c)
```

Better than before, however, we know that clusters are spherical; let's inform CEC about that.

```{r fig.width=7, fig.height=6}
c <- CEC(k=3, x=dataset, control.nstart=10, method.type='sphere')
plot(c)
```

You can learn details of clustering like this:

```{r fig.width=7, fig.height=6}
centers(c)
covMatrix(c)
```

You can predict cluster which a point would belong to:

```{r fig.width=7, fig.height=6}
predict(c, c(1,1))
```

You can visualise size and shape of clusters:

```{r fig.width=7, fig.height=6}
plot(c, ellipses=TRUE)
```

Try the same with random assignment.

```{r fig.width=7, fig.height=6}
c <- CEC(k=3, x=dataset, control.nstart=10, method.type='sphere', method.init='random')
plot(c)
```

