Cross Entropy Clustering
========================================================

Part of gmum.R project. See gmum research group page [here](http://gmum.ii.uj.edu.pl) .

General
------

CEC aims to efficiently implement Cross Entropy Clustering Algorithm as R extension.

CEC demo
------

```{r fig.width=7, fig.height=6}
library(devtools)
load_all('../')
dataset <- as.matrix(read.table("../inst/data_sets/cec/mouse_1_spherical/input.txt"))
```
That is the dataset we want to cluster
```{r fig.width=7, fig.height=6}
plot(dataset)
```

Run cec with default parameters. Set number of clusters and dataset.

```{r fig.width=7, fig.height=6}
c <- CEC(k=3, x=dataset)
plot(c)
```

Since initial clusterization is random. It may be a good idea to run cec multiple times and choose the best result.

```{r fig.width=7, fig.height=6}
c <- CEC(k=3, x=dataset, control.nstart=10)
plot(c)
```

Better than before, however, we know that clusters are spherical; let's inform cec about that.

```{r fig.width=7, fig.height=6}
c <- CEC(k=3, x=dataset, control.nstart=10, method.type='sphere')
plot(c)
```

You can learn details of clustering like this

```{r fig.width=7, fig.height=6}
centers(c)
cov(c)
```

You can predict cluster which a point would belong to

```{r fig.width=7, fig.height=6}
predictCluster(c, c(1,1))
```

or find out what are the probabilities of belonging to each cluster

```{r fig.width=7, fig.height=6}
predictClusters(c, c(1,1))
```

You can visualise size and shape of clusters

```{r fig.width=7, fig.height=6}
plot(c, ellipses=TRUE)
```

Try the same with random assignment

```{r fig.width=7, fig.height=6}
c <- CEC(k=3, x=dataset, control.nstart=10, method.type='sphere', method.init='random')
plot(c)
```
